\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Subham Patel} \\ \vspace{1pt}
    \small 908-205-4240 $|$ \href{mailto:subham.patel@rutgers.edu}{\underline{subham.patel@rutgers.edu}} $|$ 
    \href{https://github.com/Subhamp12}{\underline{github.com/Subhamp12}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \resumeSubheading
      {Rutgers University}{New Brunswick, NJ}
      {\textbf{Bachelor of Science} in Computer Science and Data Science}{}
  \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \resumeSubheading
      {UX Researcher – Google Search}{Jun. 2025 -- Aug. 2025}
      {Google -- Remote}{Contract (NDA)}
      \resumeItemListStart
        \resumeItem{Conducted research under \textbf{NDA} impacting \textbf{100M+ users} worldwide.}
      \resumeItemListEnd

    \resumeSubheading
      {Summer Intern – Genesys IVA \& Testing}{Apr. 2025 -- September 2025}
      {Pointel -- Edison, NJ (Remote)}{}
      \resumeItemListStart
        \resumeItem{Developed and enhanced \textbf{IVA solutions} serving \textbf{30M+ enterprise users}.}
        \resumeItem{Executed \textbf{500+ automated tests}, increasing release stability and reducing QA turnaround by \textbf{20\%}.}
        \resumeItem{Resolved \textbf{15+ production issues}, cutting customer downtime by \textbf{10\%}.}
        \resumeItem{Optimized test scripts to reduce runtime by \textbf{35\%}, saving \textbf{50+ engineer hours} per quarter.}
      \resumeItemListEnd

    \resumeSubheading
      {Full Stack Web Developer}{Oct. 2024 -- Apirl 2025}
      {Rutgers GRID -- New Brunswick, NJ}{}
      \resumeItemListStart
        \resumeItem{Built a scalable dashboard for \textbf{CAMILE} with \textbf{role-based authentication}, supporting \textbf{1K+ users}.}
        \resumeItem{Implemented \textbf{end-to-end Cypress testing}, reducing post-deployment bugs by \textbf{30\%}.}
        \resumeItem{Deployed secure \textbf{RESTful APIs} on \textbf{Vercel} with CI/CD pipelines, cutting release cycles from 2 weeks to \textbf{3 days}.}
        \resumeItem{Collaborated with \textbf{4+ researchers} to build interactive tools, increasing engagement by \textbf{25\%}.}
      \resumeItemListEnd
  \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
  \begin{itemize}[leftmargin=0.15in, label={}]
\resumeProjectHeading
  {\textbf{CAMILE} $|$ \emph{Next.js, Machine Learning, AI}}{Oct. 2024 -- April 2025}
  \resumeItemListStart
    \resumeItem{Developed an \textbf{AI-powered language platform} adopted by students.}
    \resumeItem{Integrated a \textbf{Next.js frontend} with a \textbf{ML backend} to adjust difficulty in real-time.}
    \resumeItem{Optimized data structures with \textbf{Prisma ORM} and \textbf{PostgreSQL}, scaling to \textbf{10K+ records}.}
    \resumeItem{Leveraged adaptive ML to improve user learning outcomes by \textbf{18\%}.}
  \resumeItemListEnd

\resumeProjectHeading
  {\textbf{Voice-to-Text Sentiment Dashboard} $|$ \emph{Python, Flask, React, Hugging Face, Whisper}}{2025}
  \resumeItemListStart
    \resumeItem{Engineered a production-ready \textbf{full-stack ML platform} that converts \textbf{customer support audio to text}, reducing manual transcription time by \textbf{95\%}.}
    \resumeItem{Implemented \textbf{NLP sentiment + emotion detection} with \textbf{BERT fine-tuning}, achieving \textbf{90\%+ F1-score} on escalation prediction.}
    \resumeItem{Deployed on \textbf{AWS (EC2, S3, Lambda)} with \textbf{Dockerized microservices}, ensuring scalable processing.}
    \resumeItem{Integrated \textbf{end-to-end CI/CD pipelines} and monitoring, enabling seamless updates with \textbf{99.9\% uptime} in cloud production.}
  \resumeItemListEnd
  \end{itemize}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, TypeScript, Python, SQL, Bash} \\
     \textbf{Frameworks \& Libraries}{: React, Next.js, Express.js, Node.js, Prisma ORM, PyTorch, TensorFlow, scikit-learn, Hugging Face Transformers} \\
     \textbf{Machine Learning}{: NLP, Sentiment Analysis, Data Pipelines, Model Deployment, MLOps (MLflow)} \\
     \textbf{Developer Tools}{: Git, Docker, Kubernetes, VS Code, Jest, Cypress, Postman, CI/CD (GitHub Actions, Jenkins)} \\
     \textbf{Databases}{: PostgreSQL, MongoDB, SQLite, Redis, Firebase} \\
     \textbf{Cloud Platforms}{: AWS (EC2, S3, Lambda, RDS), Google Cloud Platform, Vercel, Azure} \\
     \textbf{UI/UX}{: Figma, Adobe Creative Cloud, Tailwind CSS, Responsive Design} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
